---
title: "Untitled"
author: "MJ"
date: "02/04/2022"
output: html_document
---
# This part mainly examines feature selection of the most relevant predictor variables. Different methods are used including remove multicollinearity, linear regression to remove insignificant variables, Lasso


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Remove previous data from environment
rm(list = ls())
```

```{r include=FALSE}

library(arrow) # needed to read parquet file
library(plyr)
library(dplyr)
library(car)
library(caret)
library(rattle)
library(rpart.plot)
library(rpart)
library(ggplot2)
library(corrplot)
library(tidyr)
library(visdat) # to plot missing data
```

```{r}
file_path <- "../02_CleanData/policy_clean.parquet"
df <- read_parquet(file_path, as_tibble = TRUE)
#View(df)
#head(df)
```
#1 Explore 

```{r}
# Select continuous variables for correlation examination
# comment
df$ratemethodmanual <- ifelse(df$ratemethod==1, 1, 0)
df$ratemethodunderinsured <- ifelse(df$ratemethod==5, 1, 0)
# df$ratemethodprp <- ifelse(df$ratemethod==7, 1, 0) #preferered risk policy # not significant
df$elevationdifference2 <- ifelse(df$elevationdifference==999 | df$elevationdifference==9989 | df$elevationdifference==-9986, NA, df$elevationdifference)
#Policycount is the number of insured units in an active status. ==> Defined a new column: to count for 1 unit at a time
df$unitinsuredcoverage <- df$totalbuildinginsurancecoverage/df$policycount 

df_num <- subset(df, select = c(basementenclosurecrawlspacetype, censustract,crsdiscount,elevationdifference2, federalpolicyfee, latitude, longitude, policycost, policycount, reportedzipcode, totalbuildinginsurancecoverage, totalcontentsinsurancecoverage, unitinsuredcoverage))
```


```{r}
# Examine correlation between all numeric variables 
cormat <-cor(df_num, use = "pairwise.complete.obs")
```

```{r}
corrplot(cormat, tl.col = "red", tl.srt = 45, bg = "White",
         title = "\n\n Correlation Plot of Flood Insurance Data",
         type = "lower")
dev.copy(jpeg, filename="Correlation Plot of Flood Data.jpg");
dev.off ()
```


```{r}
# Looking for Spearman correlation (checks nonlinear correlation too eg y=x3 ha Spearman correlation of 1)
cormat_nonlin <- cor(df_num, use = "pairwise.complete.obs", method="spearman")
#cormat_nonlin
```

```{r}
corrplot(cormat_nonlin, tl.col = "red", tl.srt = 45, bg = "White",
         title = "\n\n Correlation Plot of Flood Data with Spearman Method",
         type = "lower")

dev.copy(jpeg, filename="Correlation Plot of Flood Data using Spearman.jpg");
dev.off ()
```

## Remove Multicollinearity with cutoff 0.6


```{r}
# Multicollinearity
# Check the variables of highly correlated

highly_corelated = findCorrelation(cormat, cutoff = 0.6)

highlyCor_Col = colnames(df_num)[highly_corelated]
highlyCor_Col

```

```{r}
# Now, we remove highly correlated variables from original dataset and create cleaner dataset, the dataset now contains 40 columns

df_clean = df[, -which(colnames(df) %in% highlyCor_Col)]
dim(df_clean)
#View(df_clean)
```

```{r}
cormat_nonlin2 <- cormat_nonlin
cormat_nonlin2[is.na(cormat_nonlin)]= 0 # replacing NA with 0
findCorrelation(cormat_nonlin2, cutoff = 0.5, names=TRUE)
```

```{r}
#totalbuildinginsurancecoverage already omitted via linear correlationmatrix
df_clean2 <- subset(df_clean, select=-c(crsdiscount, censustract, policycost)) 
```


```{r}
# Correlation Matrix for Indicator variables
df_ind <- subset(df, select = c(floodzone_highrisk, floodzone_modrisk, lowerlevelcondo, upperlevelcondo, lowerflooronly, basementandabove, basementonly, morethan1floor, ratemethodmanual, ratemethodunderinsured))

cormat_ind <-cor(df_ind, use = "pairwise.complete.obs")

corrplot(cormat_ind, tl.col = "red", tl.srt = 45, bg = "White",
         title = "\n\n Correlation Plot - Indicator Variables of Flood Insurance Data",
         type = "lower")
```

```{r}
highly_corelated_ind = findCorrelation(cormat_ind, cutoff = 0.6)
highlyCor_Col_ind = colnames(df_ind)[highly_corelated_ind]
highlyCor_Col_ind
```


```{r}
df_clean3 <- subset(df_clean2, select=-c(floodzone_modrisk)) 
dim(df_clean3)
```



```{r}
# data size is too big; cannot show it
#df_clean3 %>%
#  vis_miss(sort_miss = TRUE, warn_large_data=FALSE)
```

```{r}
# needed for next pot or it gives memory error: cannot allocate vector of size --- GB/MB')
#memory.limit(50000)
memory.limit()
```

```{r}
colnames(df_num)
```

```{r}
# Plot all the variables gaianst each other to see THEIR VISUAL RELATIONSHIP
# library(tidyr)
# have to do them one by on otherwise: memory error

ggplot(df_clean3, aes(x = basementenclosurecrawlspacetype, y = totalinsurancepremiumofthepolicy, color = floodzone_highrisk)) +
    geom_point() +
    labs(x="Basement enclosure crawl space type", y="Total Insurance Premium of the Policy" )
    theme_bw() # The classic dark-on-light ggplot2 theme
```
```{r}
ggplot(df_clean3, aes(x = construction, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE, verbose=FALSE) +
    theme_bw() # The classic dark-on-light ggplot2 theme
```

```{r}
ggplot(df_clean3, aes(x = elevationdifference2, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE, verbose=FALSE) +
    labs(x="Elevation Difference", y="Total Insurance Premium of the Policy")
    theme_bw() 
```


```{r}
ggplot(df_clean3, aes(x = totalcontentsinsurancecoverage, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE) +
    labs(x="Total Contents Insurance Coverage", y="Total Insurance Premium of the Policy" )
    theme_bw() 
```



```{r}
ggplot(df_clean3, aes(x = unitinsuredcoverage, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE) +
    labs(x="Unit Insurance Coverage", y="Total Insurance Premium of the Policy" )
    theme_bw() 
```
```{r}
ggplot(df_clean3, aes(x = longitude, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE) +
    labs(x="Longitude", y="Total Insurance Premium of the Policy" )
    theme_bw() 
```
```{r}
ggplot(df_clean3, aes(x = latitude, y = totalinsurancepremiumofthepolicy)) +
    geom_point(na.rm=TRUE) +
    labs(x="Latitude", y="Total Insurance Premium of the Policy" )
    theme_bw() 
```





```{r}
# regression should not be on dates or zipcode (which is a category not value)
tmp <- df_clean3 %>%
    select( -contains('date', ignore.case = TRUE)) %>%
    select(-c(reportedzipcode, ratemethod))

fit = lm(totalinsurancepremiumofthepolicy ~ ., data=tmp)
summary(fit)
```

## from the output, we can remove insignificant variables & some variables with NA coefficients

```{r}
tmp <- tmp %>%
    select(-c(longitude, policytermindicator, basementonly, mobilehomeortrailer, floodzone_undetermined,
              ratemethodunderinsured, elevationdifference2))

#fit1 = lm(totalinsurancepremiumofthepolicy ~. -censustract -policytermindicator -upperlevelcondo -mobilehomeortrailer #-floodzone_modrisk -floodzone_undetermined -postfirmconstructionindicator -reportedzipcode -lowerflooronly #-upperandlowerfloors -basementonly -morethan1floor -deductibleamountinbuildingcoverage, df_clean)

fit1 = lm(totalinsurancepremiumofthepolicy ~., data=tmp)
summary(fit1)
```

## Create the final dataset for further analysis

```{r}
df_final <- tmp
View(df_final)
```

```{r}
str(df_final)
```

```{r}
# scaling data
scaled_df <- as.data.frame(scale(tmp))
train_con <- trainControl(method = 'cv', number = 5) # using 5 folds cv

lasso <- train(totalinsurancepremiumofthepolicy ~., data = scaled_df,
               method = 'lasso',
               preProc = c('scale', 'center'),
               trControl = train_con,
              na.action=na.exclude)
lasso
```








```{r}
# Select only numerical columns for data analysist (leave data type in df_final)
# df_num includes 18 variables

df_num <- subset(df_final, select = -c(originalconstructiondate, originalnbdate, policyeffectivedate, policyterminationdate))

View(df_num)
```

```{r}
# categorical columns
df_cat <- subset(df_num, select = -c(latitude, longitude , policycost,policycount, totalbuildinginsurancecoverage,totalcontentsinsurancecoverage , totalinsurancepremiumofthepolicy))
lapply(df_cat, unique)

```

1. Stepwise regression

```{r}
scaledData = as.data.frame(scale(df_num[,c(6,7,10,13,14)])) # standardize all numerical variables
scaledData <- cbind(df_num[,c(1,2,3,4,5,8,9,11,12, 16, 17,18)],scaledData,df_num[,15]) # Add categorical columns  back in

colnames(scaledData)[15] <- "totalinsurancepremiumofthepolicy"
```

```{r}
ctrl <- trainControl(method = "repeatedcv", number = 5, repeats = 2)

lmFit_Step <- train(totalinsurancepremiumofthepolicy ~ ., data = scaledData, "lmStepAIC", scope = 
                 list(lower = Crime~1, upper = Crime~.), direction = "backward",trControl=ctrl,                                   na.action=na.exclude)

```



```{r}
mod_Step = lm(totalinsurancepremiumofthepolicy ~ basementenclosurecrawlspacetype + construction + crsdiscount + 
    deductibleamountincontentscoverage + elevatedbuildingindicator + 
    numberoffloorsininsuredbuilding + occupancytype + policycount + 
    primaryresidenceindicator + lowerlevelcondo + basementandabove + 
    floodzone_highrisk + latitude + longitude + totalbuildinginsurancecoverage + 
    totalcontentsinsurancecoverage,
    data = scaledData)
summary(mod_Step)
```

```{r}
## Variable selections using Lasso

train_con <- trainControl(method = 'cv', number = 5) # using 5 folds cv

lasso <- train(totalinsurancepremiumofthepolicy ~., scaledData,
               method = 'lasso',
               preProc = c('scale', 'center'),
               trControl = train_con,
              na.action=na.exclude)
lasso
```

```{r}
# Get coef

predict(lasso$finalModel, type = "coef", mode = "fraction", s = as.numeric(lasso$bestTune))

# We can further discard variables with coefficients reduced to zero
```

# From the Lasso Regression models, we can discard the variables with coeeficients near to zero, in this case is construction variables. However, in Stepwise method the construction is significant so I will keep it. # so the totalinsurancepremiumofthepolicy will have 18 variables 

```{r}
#rerun to check if there is still in-significant variables. Look like the daatset is good to go now
fit2 = lm(totalinsurancepremiumofthepolicy ~. , df_num)

summary(fit2)
```
```{r}

# Exporting the dataframe to clean folder

# df_final includes numeric (df_num) and 4 "date" columns

file_path3 <- "../03_EDA/df_final.parquet"
write_parquet(df_final, file_path3)

# df_num includes only numeric variables for analysis
file_path4 <- "../03_EDA/df_num.parquet"
write_parquet(df_num, file_path4)

```

