---
title: "Untitled"
author: "MJ"
date: "02/04/2022"
output: html_document
---
# This part mainly examines feature selection of the most relevant predictor variables. Different methods are used including remove multicollinearity, linear regression to remove insignificant variables, Lasso


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Remove previous data from environment
rm(list = ls())
```

```{r}
library(arrow) # needed to read parquet file
library(dplyr)
library(car)
library(caret)
library(ggplot2)
library(corrplot)
```

```{r}
file_path <- "../02_CleanData/policy_clean.parquet"
df <- read_parquet(file_path, as_tibble = TRUE)
head(df)

```

```{r}
str(df)
```
```{r}
# Select continuous variables for correlation examination
# comment
df_num <- subset(df, select = c(basementenclosurecrawlspacetype, censustract,crsdiscount,elevationdifference,federalpolicyfee, latitude, longitude, policycost, policycount, reportedzipcode, ratemethod, totalbuildinginsurancecoverage, totalcontentsinsurancecoverage))

# Examine correlation between all numeric variables

cormat <-cor(df_num, use = "pairwise.complete.obs")
cormat
```
```{r}
corrplot(cormat)
```

```{r}
# Looking for Spearman correlation (checks nonlinear correlation too eg y=x3 ha Spearman correlation of 1)
cormat_nonlin <- cor(df_num, use = "pairwise.complete.obs", method="spearman")
cormat_nonlin
```

```{r}
corrplot(cormat_nonlin)
```

## check Multicollinearity


```{r}
# Multicollinearity
# Check the variables of highly correlated

highly_corelated = findCorrelation(cormat, cutoff = 0.6)

highlyCor_Col = colnames(df_num)[highly_corelated]
highlyCor_Col

```

```{r}
# Now, we remove highly correlated variables from original dataset and create cleaner dataset

df_clean = df[, -which(colnames(df) %in% highlyCor_Col)]
dim(df_clean)

```
```{r}
fit = lm(totalinsurancepremiumofthepolicy ~., df_clean)
summary(fit)
```
## from the output, we can remove some insignificant variables, but keep lattitude and reportedzipcode for mapping the areas where flood occurs

```{r}
fit1 = lm(totalinsurancepremiumofthepolicy ~. -censustract -policytermindicator -upperlevelcondo -mobilehomeortrailer -floodzone_modrisk -floodzone_undetermined, df_clean)
summary(fit1)
```

## Create the final dataset for further analysis

```{r}
df_final <- subset(df_clean, select = -c(censustract,policytermindicator,mobilehomeortrailer, upperlevelcondo,floodzone_modrisk,floodzone_undetermined))

View(df_final)
```


```{r}
str(df_final)

# Select only numerical columns for data analysist
df_num <- subset(df_final, select = -c(originalconstructiondate, policyeffectivedate, policyterminationdate))
```

```{r}
## Variable selections using Lasso

train_con <- trainControl(method = 'cv', number = 5) # using 5 folds cv

lasso <- train(totalinsurancepremiumofthepolicy ~., df_num,
               method = 'lasso',
               preProc = c('scale', 'center'),
               trControl = train_con,
               na.action=na.exclude)
lasso


```