---
title: "Untitled"
author: "MJ"
date: "02/04/2022"
output: html_document
---
# This part mainly examines feature selection of the most relevant predictor variables. Different methods are used including remove multicollinearity, linear regression to remove insignificant variables, Lasso


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Remove previous data from environment
rm(list = ls())
```

```{r}
library(arrow) # needed to read parquet file
library(plyr)
library(dplyr)
library(car)
library(caret)
library(ggplot2)
library(corrplot)
```

```{r}
file_path <- "../02_CleanData/policy_clean.parquet"
df <- read_parquet(file_path, as_tibble = TRUE)
head(df)

```

```{r}
str(df)
```
```{r}
# Select continuous variables for correlation examination
# comment
df_num <- subset(df, select = c(basementenclosurecrawlspacetype, censustract,crsdiscount,elevationdifference,federalpolicyfee, latitude, longitude, policycost, policycount, reportedzipcode, ratemethod, totalbuildinginsurancecoverage, totalcontentsinsurancecoverage))

```


```{r}
# Examine correlation between all numeric variables
cormat <-cor(df_num, use = "pairwise.complete.obs")

corrplot(cormat, tl.col = "red", tl.srt = 45, bg = "White",
         title = "\n\n Correlation Plot Of Gambling Data",
         type = "lower")

```
```{r}
#cormat <-cor(df_num, use = "pairwise.complete.obs")

#corrplot(cormat)
```




```{r}
# Looking for Spearman correlation (checks nonlinear correlation too eg y=x3 ha Spearman correlation of 1)
cormat_nonlin <- cor(df_num, use = "pairwise.complete.obs", method="spearman")
cormat_nonlin
```

```{r}
corrplot(cormat_nonlin)
```

## check Multicollinearity


```{r}
# Multicollinearity
# Check the variables of highly correlated

highly_corelated = findCorrelation(cormat, cutoff = 0.6)

highlyCor_Col = colnames(df_num)[highly_corelated]
highlyCor_Col

```

```{r}
# Now, we remove highly correlated variables from original dataset and create cleaner dataset

df_clean = df[, -which(colnames(df) %in% highlyCor_Col)]
dim(df_clean)

```
```{r}
fit = lm(totalinsurancepremiumofthepolicy ~., df_clean)
summary(fit)
```
## from the output, we can remove some insignificant variables, but keep lattitude and reportedzipcode for mapping the areas where flood occurs

```{r}
fit1 = lm(totalinsurancepremiumofthepolicy ~. -censustract -policytermindicator -upperlevelcondo -mobilehomeortrailer -floodzone_modrisk -floodzone_undetermined, df_clean)
summary(fit1)
```

## Create the final dataset for further analysis

```{r}
df_final <- subset(df_clean, select = -c(censustract,policytermindicator,mobilehomeortrailer, upperlevelcondo,floodzone_modrisk,floodzone_undetermined))

View(df_final)
```

```{r}
str(df_final)
```


```{r}
# Select only numerical columns for data analysist (leave data type in df_final)
# df_num inlcudes 25 variables

df_num <- subset(df_final, select = -c(originalconstructiondate, originalnbdate, policyeffectivedate, policyterminationdate))

View(df_num)
```

```{r}
## Variable selections using Lasso

train_con <- trainControl(method = 'cv', number = 5) # using 5 folds cv

lasso <- train(totalinsurancepremiumofthepolicy ~., df_num,
               method = 'lasso',
               preProc = c('scale', 'center'),
               trControl = train_con,
              na.action=na.exclude)
lasso
```

```{r}
# Get coef

predict(lasso$finalModel, type = "coef", mode = "fraction", s = as.numeric(lasso$bestTune))

# We can further discard variables with coefficients reduced to zero
```

# From the Lasso Regression models, we can discard the variables with coeeficients near to zero, so the totalinsurancepremiumofthepolicy will mainly depends on 7 variables as folows: totalinsurancepremiumofthepolicy ~ deductibleamountincontentscoverage, federalpolicyfee, totalbuildinginsurancecoverage, totalcontentsinsurancecoverage, primaryresidenceindicator, policycost, floodzone_highrisk 



```{r}

# Exporting the dataframe to clean folder

# df_final includes "date" columns

file_path3 <- "../03_EDA/df_final.parquet"
write_parquet(df_final, file_path3)

# df_num includes only numeric variables for analysis
file_path4 <- "../03_EDA/df_num.parquet"
write_parquet(df_num, file_path4)

# df includes only 7 predicted variables and response as suggested by Lasso for analysis

df <- subset(df_num, select = c(totalinsurancepremiumofthepolicy, deductibleamountincontentscoverage, federalpolicyfee, totalbuildinginsurancecoverage, totalcontentsinsurancecoverage, primaryresidenceindicator, policycost, floodzone_highrisk))
                                       
file_path5 <- "../03_EDA/df.parquet"
write_parquet(df, file_path5)

```

## Move to the next section of modeling

```{r}
file_path <- "../03_EDA/df.parquet"
df <- read_parquet(file_path, as_tibble = TRUE)
#View(df)
```

```{r}
corr_plot <-cor(df, use = "pairwise.complete.obs")

corrplot(corr_plot, tl.col = "red", tl.srt = 45, bg = "White",
         title = "\n\n Correlation Plot Of Gambling Data",
         type = "lower")
```

# Part 1: Supervised classification model

```{r}
fit = lm(totalinsurancepremiumofthepolicy ~., df)
summary(fit)
```


### Decision Tree

```{r}
set.seed(99)

df[is.na(df)] = 0 #replace NA with 0

Train = createDataPartition(df$totalinsurancepremiumofthepolicy, p=0.75, list=FALSE)
#split data in 75%-25% ratio

training = df[ Train, ] #75% data for training 
testing = df[ -Train, ] #25% testing

# define training control
train_control <- trainControl(method="cv", number=10)
#10 fold cv


fit1= train(totalinsurancepremiumofthepolicy~., data=df, method="rpart",
            trControl=train_control)

fit1

fancyRpartPlot(fit1$finalModel)

summary(fit1)

#### which are the important variables

varImp(fit1)

summary(df)

plot(varImp(fit1), top = 5)

########## predict on unseen data

pred1 = predict(fit1, testing)

confusionMatrix(pred1, testing$loan_status)
```



















