---
title: "CleanData"
author: "MJ"
date: "24/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Remove previous data from environment
rm(list = ls())
```

```{r}
library(arrow) # needed to read parquet file
library(dplyr)
```


## Read & View the Data
```{r}
# path to the project folder
#setwd("C:/Users/mjafarpour/Downloads/MGT_6203_GroupProject/")
file_path <- "../01_RawData/nfip_Houston_flood_policies.parquet"
policy_df <- read_parquet(file_path, as_tibble = TRUE)
head(policy_df)
```

## I filter the dataset again for Texas only 
```{r}
## Filter propertystate = 'TX"
policy_df <- subset(policy_df, propertystate == 'TX' )
```


```{r}
policy_df = subset(policy_df,select=-c(agriculturestructureindicator, propertystate, reportedcity, houseofworshipindicator,nonprofitindicator,regularemergencyprogramindicator,smallbusinessindicatorbuilding,hfiaasurcharge))
View(policy_df)
```

```{r}
# count NA values in each column
colSums(is.na(policy_df))
```

## Continue fiter some columns with large number of NA

```{r}
# Filter more columns with significant number of NA values
policy_df = subset(policy_df,select=-c(basefloodelevation,cancellationdateoffloodpolicy, countycode, elevationcertificateindicator, lowestadjacentgrade, lowestfloorelevation, obstructiontype))                          
View(policy_df)
```

```{r}
# Number of NA values in each column
colSums(is.na(policy_df))
```
```{r}
## Observe unique value in each column
count_unique <- rapply(policy_df, function(x) length(unique(x)))
count_unique
```


```{r}

policy_df$postfirmconstructionindicator=ifelse(policy_df$postfirmconstructionindicator=='Y',1,0)
policy_df$primaryresidenceindicator=ifelse(policy_df$primaryresidenceindicator=='Y',1,0)
policy_df$elevatedbuildingindicator=ifelse(policy_df$elevatedbuildingindicator=='Y',1,0)
policy_df$construction=ifelse(policy_df$construction=='Y',1,0)

#condominum indicator for lower level and upper level condo
policy_df$lowerlevelcondo=ifelse(policy_df$condominiumindicator=='L',1,0)
policy_df$upperlevelcondo=ifelse(policy_df$condominiumindicator=='U',1,0)

#trying to factor the locationofcontents column ....feel free to advise anyother column names. 
policy_df$lowerflooronly=ifelse(policy_df$locationofcontents=='Lowest floor only above ground level (No basement/enclosure/crawlspace/subgrade crawlspace)',1,0)
policy_df$upperandlowerfloors=ifelse(policy_df$locationofcontents=='Lowest floor above ground level and higher floors (No basement/enclosure/crawlspace/subgrade crawlspace)',1,0)
policy_df$basementandabove=ifelse(policy_df$locationofcontents=='Basement/Enclosure/Crawlspace/Subgrade Crawlspace and above',1,0)
policy_df$basementonly=ifelse(policy_df$locationofcontents=='Basement/Enclosure/Crawlspace/Subgrade Crawlspace only',1,0)
policy_df$morethan1floor=ifelse(policy_df$locationofcontents=='Above ground level more than one full floor',1,0)
policy_df$mobilehomeortrailer=ifelse(policy_df$locationofcontents==' Manufactured (mobile) home or travel trailer on foundation',1,0)

#dropping the following columns as being empty or not relevent/required. feel free to comment if not the right thing to do
policy_df=subset(policy_df,select=-c(agriculturestructureindicator,houseofworshipindicator,nonprofitindicator,regularemergencyprogramindicator,smallbusinessindicatorbuilding,hfiaasurcharge))


