---
title: "CleanData"
author: "MJ"
date: "24/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Remove previous data from environment
rm(list = ls())
```

```{r include=FALSE}
library(arrow) # needed to read parquet file
library(dplyr)
library(car)
library(caret)
library(ggplot2)
library(corrplot)
```

## Read & View the Data
```{r}
# path to the project folder
#setwd("C:/Users/mjafarpour/Downloads/MGT_6203_GroupProject/")
file_path <- "../01_RawData/nfip_Houston_flood_policies.parquet"
policy_df1 <- read_parquet(file_path, as_tibble = TRUE)
#head(policy_df1)
```

## Filter the dataset again for Texas only 
```{r}
## Filter propertystate = 'TX"
policy_df1 <- subset(policy_df1, propertystate == 'TX' )
```


```{r}
policy_df = subset(policy_df1,select=-c(agriculturestructureindicator, propertystate, reportedcity, houseofworshipindicator,nonprofitindicator,regularemergencyprogramindicator,smallbusinessindicatorbuilding,hfiaasurcharge))
#View(policy_df)
```

```{r}
# count NA values in each column
colSums(is.na(policy_df))
```

## Continue fiter some columns with large number of NA (over 60%) and irrelevant variables

```{r}
# Filter more columns with significant number of NA values
policy_df = subset(policy_df,select=-c(basefloodelevation,cancellationdateoffloodpolicy, countycode, elevationcertificateindicator, lowestadjacentgrade, lowestfloorelevation, obstructiontype))                          
View(policy_df)
```

```{r}
# Number of NA values in each column
colSums(is.na(policy_df))
```
```{r}
## Observe unique value in each column

categorical_col <- policy_df[c("condominiumindicator", "construction", "elevatedbuildingindicator", "floodzone", "locationofcontents", "postfirmconstructionindicator", "primaryresidenceindicator")]

count_unique <- rapply(categorical_col, function(x) length(unique(x)))
count_unique
```
## Some category variable neeed to clarify:
## condominiumindicator (6), construction (3), elevatedbuildingindicator(3), floodzone (33), locationofcontents (7), postfirmconstructionindicator (3), primaryresidenceindicator (3)
```{r}
# condominiumindicator variables
unique(policy_df$condominiumindicator)

```

```{r}
unique(policy_df$locationofcontents)
```


```{r}
unique(policy_df$construction)
unique(policy_df$elevatedbuildingindicator)
unique(policy_df$postfirmconstructionindicator)
unique(policy_df$primaryresidenceindicator)
```

```{r}
#condominum indicator for what type of condominium, 95% for not a condominium (N), 3% for U and 3% for other
policy_df$not_condo=ifelse(policy_df$condominiumindicator=='N',1,0)
policy_df$u_condo=ifelse(policy_df$condominiumindicator=='U',1,0)

# Construction
policy_df$construction=ifelse(policy_df$construction=='Y',1,0)

#imputing locationofcontents with mode
val <- unique(policy_df$locationofcontents[!is.na(policy_df$locationofcontents)])                   
my_mode <- val[which.max(tabulate(match(policy_df$locationofcontents, val)))]
policy_df$locationofcontents[is.na(policy_df$locationofcontents)]=my_mode

#imputing locationofcontents with 0
policy_df$locationofcontents[is.na(policy_df$locationofcontents)]=0

#imputing the deductibles column
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='0']=500
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='1']=1000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='2']=2000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='3']=3000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='4']=4000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='5']=5000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='9']=750
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='A']=10000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='B']=15000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='C']=20000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='D']=25000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='E']=50000
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='F']=1250
policy_df$deductibleamountincontentscoverage[policy_df$deductibleamountincontentscoverage=='G']=1500

policy_df$deductibleamountincontentscoverage[is.na(policy_df$deductibleamountincontentscoverage)]=0


policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='0']=500
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='1']=1000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='2']=2000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='3']=3000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='4']=4000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='5']=5000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='9']=750
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='A']=10000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='B']=15000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='C']=20000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='D']=25000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='E']=50000
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='F']=1250
policy_df$deductibleamountinbuildingcoverage[policy_df$deductibleamountinbuildingcoverage=='G']=1500

policy_df$deductibleamountinbuildingcoverage[is.na(policy_df$deductibleamountinbuildingcoverage)]=0

#elevatedbuildingindicator
policy_df$elevatedbuildingindicator=ifelse(policy_df$elevatedbuildingindicator=='Y',1,0)


#Factor the locationofcontents column 
policy_df$lowerflooronly=ifelse(policy_df$locationofcontents=='Lowest floor only above ground level (No basement/enclosure/crawlspace/subgrade crawlspace)',1,0)
policy_df$upperandlowerfloors=ifelse(policy_df$locationofcontents=='Lowest floor above ground level and higher floors (No basement/enclosure/crawlspace/subgrade crawlspace)',1,0)
policy_df$basementandabove=ifelse(policy_df$locationofcontents=='Basement/Enclosure/Crawlspace/Subgrade Crawlspace and above',1,0)
policy_df$basementonly=ifelse(policy_df$locationofcontents=='Basement/Enclosure/Crawlspace/Subgrade Crawlspace only',1,0)
policy_df$morethan1floor=ifelse(policy_df$locationofcontents=='Above ground level more than one full floor',1,0)
policy_df$mobilehomeortrailer=ifelse(policy_df$locationofcontents==' Manufactured (mobile) home or travel trailer on foundation',1,0)

#postfirmconstructionindicator
policy_df$postfirmconstructionindicator=ifelse(policy_df$postfirmconstructionindicator=='Y',1,0)

#primaryresidenceindicator
policy_df$primaryresidenceindicator=ifelse(policy_df$primaryresidenceindicator=='Y',1,0)
```

```{r}
View(policy_df)
```


```{r}
# Continue remove category variables which have been replaced as above

df = subset(policy_df,select=-c(condominiumindicator, construction, elevatedbuildingindicator, locationofcontents, postfirmconstructionindicator, primaryresidenceindicator))
View(df)
```


```{r}
## Type of data in all columns
str(df)
```
```{r}
# Convert all date from numeric to date format

date_cols <- c("originalconstructiondate", "originalnbdate", "policyeffectivedate", "policyterminationdate")

df1 <- df %>%
   mutate_at(vars(all_of(date_cols)), funs(as.Date(., "%Y-%m-%d")))

#str(df1)
```

```{r}
#floodzones
# high risk if starts with A or V
df1$floodzone_highrisk <- ifelse( (startsWith(df1$floodzone, 'A') | (startsWith(df1$floodzone, 'V'))),1,0)
# moderate-to-low risk if starts with B, C or X
df1$floodzone_modrisk <- ifelse( (startsWith(df1$floodzone, 'B') | (startsWith(df1$floodzone, 'C')) | (startsWith(df1$floodzone, 'X'))),1,0)
# possible but undetermined flood hazards: starts with D
df1$floodzone_undetermined <- ifelse( (startsWith(df1$floodzone, 'D')) ,1,0)
```


```{r}
#identify all character columns
df2 <- subset(df1, select = -c(floodzone))
# ratemethod should also be categorical; 1 - Manual 2 - Specific 3 - Alternative 4 - V-Zone Risk Factor Rating Form 5 - Underinsured Condominium Master Policy 6 - Provisional 7 - Preferred Risk Policy (PRPs issued for eligible properties located within a non-Special Flood Hazard Area [non-SFHA]) 8 - Tentative 9 - MPPP Policy 

chars <- sapply(df2, is.character)

#convert all character columns to numeric
df2[ , chars] <- as.data.frame(apply(df2[ , chars], 2, as.numeric))
str(df2)
```

```{r}
# Remove negative value
df2 <- df2[df2$policycost >= 0, ]
df2 <- df2[df2$federalpolicyfee >= 0, ]
df2 <- df2[df2$totalinsurancepremiumofthepolicy >= 0, ]
```

# Examine the response variable (totalinsurancepremiumofthepolicy)

```{r}
summary(df2$totalinsurancepremiumofthepolicy)
```

```{r}
ggplot(df2, aes(x = totalinsurancepremiumofthepolicy, fill = cut(x=totalinsurancepremiumofthepolicy, 100))) +
  geom_histogram(show.legend = FALSE) +
  scale_fill_discrete(h = c(240, 10), c = 120, l = 70) +
  theme_minimal() +
  labs(x = "Total Insurance Premium", y = "Frequency") +
  ggtitle("Histogram of Total Insurance Premium")

dev.copy(jpeg,filename="Histogram of Total Insurance Premium_Original.jpg");
dev.off ()

```

```{r}
summary(df2$totalinsurancepremiumofthepolicy)
ggplot(data = df2, aes(x=totalinsurancepremiumofthepolicy)) + geom_density(alpha = 0.5)+
        labs(x = "Total Insurance Premium", y = "Frequency")+
                ggtitle("Distribution of Insurance Premium")

dev.copy(jpeg,filename="Distribution of Total Insurance Premium_Original.jpg");
dev.off ()
```



```{r}
# As the number of totalinsurancepremiumofthepolicy > 5000 is only 0.1% then we remove all rows with the value higher than 5000 to eleminate error

df2 <- df2[(df2$totalinsurancepremiumofthepolicy < 3000),]

```
```{r}
ggplot(df2, aes(x = totalinsurancepremiumofthepolicy, fill = cut(x=totalinsurancepremiumofthepolicy, 100))) +
  geom_histogram(show.legend = FALSE) +
  scale_fill_discrete(h = c(240, 10), c = 120, l = 70) +
  theme_minimal() +
  labs(x = "Total Insurance Premium", y = "Frequency") +
  ggtitle("Histogram of Total Insurance Premium")

dev.copy(jpeg,filename="Histogram of Total Insurance Premium_Final.jpg");
dev.off ()
```


```{r}
View(df2)
```



```{r}
summary(df2$totalinsurancepremiumofthepolicy)
ggplot(data = df2, aes(x=totalinsurancepremiumofthepolicy)) + geom_density(alpha = 0.5)+
        labs(x = "Total Insurance Premium", y = "Frequency")+
                ggtitle("Distribution of Insurance Premium")

dev.copy(jpeg,filename="Distribution of Total Insurance Premium_Final.jpg");
dev.off ()
```


```{r}
# Exporting the dataframe to clean folder
file_path2 <- "../02_CleanData/policy_clean.parquet"
write_parquet(df2, file_path2)
```

